---
title: "LMwithPred"
author: "Jeannet Cendejas"
date: "11/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction  
This is the linear model with prediction problem. Predict strength scores using data from the following website  

```{r}
dataF <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt", sep="", header=TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
require(ggplot)
```

$H_O$: The null hypothesis states that there is no difference in these models; either one is just as good as the other.  
$H_A$: The alternative hypothesis states that there is a difference in these models; one is better than the others.  

### Plot Scatterplot

```{r}
plot(SIMS~ARM,data=dataF)
```

```{r}
basicNN <- ggplot(dataF,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

```{r}
model.1 <- lm(SIMS~ARM,data=dataF)
summary.lm(model.1)
new=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,new,interval = "prediction")
```

##  
```{r}
plot(SIMS~GRIP,data=dataF)
```
```{r}
basicNN <- ggplot(dataF,aes(y=SIMS,x=GRIP))
```
##Now add in scatterplot

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

```{r}
model.2 <- lm(SIMS~GRIP,data=dataF)
summary.lm(model.2)
predict.lm(model.2,new,interval = "prediction")
``` 

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=dataF)
summary.lm(model.3)
predict.lm(model.3,new,interval = "prediction")
```

```{r}
anova(model.1,model.3)
```

## Conclusion
Based on the p-value which is 0.000004, we reject the null hypothesis and conclude as we saw with the adjusted r-squared that model 2 is the better predictor than model 1.